Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-10 cvpr2018.tex
vs similarity

Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
\textcolor{red}{In the spirit of variational auto-encoder \cite{} and the practice of \cite{han2017stackgan} (namely conditional augmentation), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$. We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the $G$ loss to force smooth sampling over the text embedding distribution. }

@@

\textbf{Evaluation metric}
We use three different quantitative metrics to evaluate our method.
%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
% \begin{equation}
%	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
% \end{equation}
% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. 
1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality. For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN. For MS COCO dataset, we directly use the model train on ImageNet.
2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance.
\textcolor{red}{3) Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, namely neural image-sentence distance, which calculated the cosine distance between image code and the sentence vector. We train the model on each dataset. }

@@

%\begin{table}[t] % retrieval
%	\begin{center}
%		\begin{tabularx}{.42\textwidth}{c|ccc}
%			\specialrule{1.5pt}{0pt}{0pt}  
%			Scale 						& StackGAN & HDGAN & HR Test					\\ 				\hline
%            $64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ &  ${3.46{\pm}.04}$	\\
%           $128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$	& ${3.45{\pm}.04}$	\\
%           $256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ & ${3.46{\pm}.04}$ \\ \hline
%		\end{tabularx}
%	\end{center} \vspace{-.4cm}
%	\caption{Scale accuracy \textcolor{red}{changing to figure is better}.} \label{table:multiscales}
%\end{table}
\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.32\textwidth}{c|cc}
			\specialrule{1.5pt}{0pt}{0pt}  
			Scale 						& StackGAN & HDGAN 					\\ 				\hline
			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ \\
			$128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$		\\
			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ \\ \hline
		\end{tabularx}
	\end{center} \vspace{-.4cm}
	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
\end{table}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on CUB} \label{fig:vis-cub}
\end{figure}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on Oxford} \label{fig:vis-oxford}
\end{figure}

@@

@@

\subsection{On the Local Image Loss}
\begin{table}[t] % retrieval
	\label{tab:local_loss}
	\begin{center}
		\begin{tabularx}{.32\textwidth}{c|cc}
			\specialrule{1.5pt}{0pt}{0pt}  
			Scale 						&   No Local 	& With Local				\\ 				\hline
			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ \\
			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ \\ \hline
		\end{tabularx}
	\end{center} \vspace{-.4cm}
	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:imgloss}
\end{table}

@@

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.268\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\

>>>>

Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of \cite{han2017stackgan} (namely conditional augmentation), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$. We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the $G$ loss to force smooth sampling over the text embedding distribution. }

@@

\textbf{Evaluation metric}
We use three different quantitative metrics to evaluate our method.
%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
% \begin{equation}
%	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
% \end{equation}
% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. 
1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality. For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN. For MS COCO dataset, we directly use the model pre-trained on ImageNet.
2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance.

\textbf{Visual-semantic similarity~}
Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description. We introduce a new qualitative measurement, namely neural visual-semantic similarity (VS similarity) \cite{vsemb}. Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding. 
We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
We learn two mapping functions $f_v$ and $f_t$, which map the image and sentence embeddings into one semantic space, using the following bi-directional ranking loss:
\begin{equation}
\begin{split}
\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
\end{split}
\end{equation}
where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $v$, and vice-versa for $\bm{v^-}$. In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.

@@

%\begin{table}[t] % retrieval
%	\begin{center}
%		\begin{tabularx}{.42\textwidth}{c|ccc}
%			\specialrule{1.5pt}{0pt}{0pt}  
%			Scale 						& StackGAN & HDGAN & HR Test					\\ 				\hline
%            $64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ &  ${3.46{\pm}.04}$	\\
%           $128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$	& ${3.45{\pm}.04}$	\\
%           $256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ & ${3.46{\pm}.04}$ \\ \hline
%		\end{tabularx}
%	\end{center} \vspace{-.4cm}
%	\caption{Scale accuracy \textcolor{red}{changing to figure is better}.} \label{table:multiscales}
%\end{table}
\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.32\textwidth}{c|cc}
			\specialrule{1.5pt}{0pt}{0pt}
			Scale 						& StackGAN & HDGAN 					\\ 				\hline
			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ \\
			$128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$		\\
			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.15{\pm}.05}$ \\ \hline
		\end{tabularx}
	\end{center} \vspace{-.4cm}
	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
\end{table}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on CUB} \label{fig:vis-cub}
\end{figure}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on Oxford} \label{fig:vis-oxford}
\end{figure}

@@

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.477\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
						&	 CUB		&	Oxford  & COCO		     \\ \hline
			StackGAN     &	$0.234{\pm}.167$	&	 $0.278{\pm}.134$			&  $-{\pm}-$		\\

			Ground Truth	&	${0.302{\pm}.151}$	&	$ {0.336{\pm}.138}$			&  -  \\ \hline
			HDGAN 		&	$\bm{0.259{\pm}.159}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
		\end{tabularx} \vspace{-.4cm}
	\end{center}
	\caption{The visual-semantic similarity evaluation on three datasets. The higher score represents higher degree of matching between the generated images and the text information. } \label{table:score}
\end{table}

@@

\subsection{On the Local Image Loss}
\begin{table}[t] % retrieval
	\label{tab:local_loss}
	\begin{center}
		\begin{tabularx}{.36\textwidth}{c|cc}
			\specialrule{1.5pt}{0pt}{0pt}  
			Metric 					&   No Local 	       &    With Local	\\  \hline
			MS-SSMI                 &   $-$                &	$0.215$ \\  \hline
			VS similarity           &   $-$                &	$0.259{\pm}.159$ \\ \hline
			Inception score         &   $-$   &  	$4.15{\pm}.05$ \\
		\end{tabularx}
	\end{center} \vspace{-.4cm}
	\caption{Results using three quantitative evaluation metrics on birds dataset.} \label{table:imgloss}
\end{table}

@@

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.268\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\
